Manuscript progress report

### 2024-07-19 Docs/manuscript.Rmd
figures with prediction interval

set.seed(1120)

@@

## prediction window 
window <- seq(0, 1, by = 0.2)
M <- 500

@@

```{r load_sim1}
load(here("Data/SimOutput_fGFPCA.RData"))
load(here("Data/SimOutput_GLMMadaptive.RData"))
load(here("Data/SimOutput_GFOSR_L1.RData"))
pred_list_gfosr_l1 <- pred_list_gfofr
t_vec_gfosr_l1 <- t_vec_gfofr
rm(pred_list_gfofr, t_vec_gfofr)
load(here("Data/SimOutput_GFOSR_L5.RData"))
pred_list_gfosr_l5 <- pred_list_gfofr
t_vec_gfosr_l5 <- t_vec_gfofr
rm(pred_list_gfofr, t_vec_gfofr)

@@

```{r fig_large_sim_paper, fig.height=8, fig.width=8}
bind_rows(
  pred_list_all[[1]] %>% filter(id %in% rand_id) %>% 
    mutate(method="fGFPCA"),
  pred_list_ref[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GLMMadaptive"),
  pred_list_gfosr_l1[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=1)") %>%
    rename(pred0.2=pred_w1, pred0.4=pred_w2, pred0.6=pred_w3, pred0.8=pred_w4),
  pred_list_gfosr_l5[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=5)") %>%
    rename(pred0.2=pred_w1, pred0.4=pred_w2, pred0.6=pred_w3, pred0.8=pred_w4)
) %>% mutate_at(vars(eta_i, pred0.2, pred0.4, pred0.6, pred0.8), 
                .funs = function(x){exp(x)/(1+exp(x))}) %>%
  mutate(method=factor(method, 
         levels = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"))) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"), linetype = "dashed")+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), na.rm=T, linewidth = 1.0)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), na.rm=T, linewidth = 1.0)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), na.rm=T, linewidth = 1.0)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), na.rm=T, linewidth = 1.0)+
  facet_grid(rows = vars(id), cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "bottom")+
  scale_color_manual(values = cols)
```

## ISE and AUC

```{r ise}
## ISE container 
ise_fgfpca <- ise_adglmm <- ise_gfosr_l1 <- ise_gfosr_l5 <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M))
# dims: prediction window, max obs time, simulation iter

@@

```{r ise_fGFPCA}
## calculation
for(m in 1:M){
  # this_df <- pred_list_all[[m]]
  ise_tb <- pred_list_all[[m]] %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err"))
  ise_fgfpca[, ,m] <- as.matrix(ise_tb)

}

mean_ise_fgfpca <- apply(ise_fgfpca, c(1, 2), mean)

# mean_ise <- data.frame(mean_ise) %>%
#   mutate(Window = c("(0.2, 0.4]", "(0.4, 0.6]", "(0.6, 0.8]", "(0.8, 1.0]"),
#          .before = 1)
colnames(mean_ise_fgfpca) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r ise_adglmm}
## calculation
for(m in 1:M){
  # this_df <- pred_list_gfosr_l1[[m]]
  ise_tb <- pred_list_ref[[m]] %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err"))
  ise_adglmm[, ,m] <- as.matrix(ise_tb)
}

mean_ise_adglmm <- apply(ise_adglmm, c(1, 2), mean)
colnames(mean_ise_adglmm) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r ise_gfosr_l1}
## calculation
for(m in 1:M){
  # this_df <- pred_list_ref[[m]]
  ise_tb <- pred_list_gfosr_l1[[m]] %>%
    mutate(err1 = (pred_w1-eta_i)^2,
           err2 = (pred_w2-eta_i)^2,
           err3 = (pred_w3-eta_i)^2,
           err4 = (pred_w4-eta_i)^2) %>%
    select(id, t, starts_with("err"), window) %>% 
    # mutate(window = factor(window, levels = 1:5, 
    #                        labels = c("[0,0.2]", "(0.2,0.4]", "(0.4,0.6]",))) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != 1) %>% 
    select(starts_with("err"))
  ise_gfosr_l1[, ,m] <- as.matrix(ise_tb)
}

mean_ise_gfosr_l1 <- apply(ise_gfosr_l1, c(1, 2), mean)
colnames(mean_ise_gfosr_l1) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r ise_gfosr_l5}
## calculation
for(m in 1:M){
  # this_df <- pred_list_ref[[m]]
  ise_tb <- pred_list_gfosr_l5[[m]] %>%
    mutate(err1 = (pred_w1-eta_i)^2,
           err2 = (pred_w2-eta_i)^2,
           err3 = (pred_w3-eta_i)^2,
           err4 = (pred_w4-eta_i)^2) %>%
    select(id, t, starts_with("err"), window) %>% 
    # mutate(window = factor(window, levels = 1:5, 
    #                        labels = c("[0,0.2]", "(0.2,0.4]", "(0.4,0.6]",))) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != 1) %>% 
    select(starts_with("err"))
  ise_gfosr_l5[, ,m] <- as.matrix(ise_tb)
}

mean_ise_gfosr_l5 <- apply(ise_gfosr_l5, c(1, 2), mean)
colnames(mean_ise_gfosr_l5) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r auc_func}
## a function to calculate AUC
get_auc <- function(y, pred){
  if(sum(is.na(y))>0 | sum(is.na(pred))>0){
    auc <- NA
  }
  else{
    this_perf <- performance(prediction(pred, y), measure = "auc")
    auc <- this_perf@y.values[[1]]
  }
  return(auc)
}

```{r}
## auc container 
auc_fgfpca <- auc_adglmm <- auc_gfosr_l1 <- auc_gfosr_l5 <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M))
```

```{r auc_fGFPCA}
for(m in 1:M){
  this_df <- pred_list_all[[m]]
  auc_tb <- this_df %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    select(Y, starts_with("pred"), window) %>%
    group_by(window) %>%
    summarise(auc1 = get_auc(Y, pred0.2),
              auc2 = get_auc(Y, pred0.4),
              auc3 = get_auc(Y, pred0.6),
              auc4 = get_auc(Y, pred0.8)) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("auc"))
  auc_fgfpca[, ,m] <- as.matrix(auc_tb)
}

mean_auc_fgfpca <- apply(auc_fgfpca, c(1, 2), mean)
# mean_auc <- data.frame(mean_auc) %>% 
#   mutate(Window = c("(0.2, 0.4]", "(0.4, 0.6]", "(0.6, 0.8]", "(0.8, 1.0]"),
#          .before = 1)
colnames(mean_auc_fgfpca) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r auc_GLMMadaptive}
for(m in 1:M){
  this_df <- pred_list_ref[[m]]
  auc_tb <- this_df %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    select(Y, starts_with("pred"), window) %>%
    group_by(window) %>%
    summarise(auc1 = get_auc(Y, pred0.2),
              auc2 = get_auc(Y, pred0.4),
              auc3 = get_auc(Y, pred0.6),
              auc4 = get_auc(Y, pred0.8)) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("auc"))
  auc_adglmm[, ,m] <- as.matrix(auc_tb)

}

mean_auc_adglmm <- apply(auc_adglmm, c(1, 2), mean)
colnames(mean_auc_adglmm) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r auc_gfosr_l1}
for(m in 1:M){
  this_df <- pred_list_gfosr_l1[[m]]
  auc_tb <- this_df %>% 
    select(Y, starts_with("pred"), window) %>%
    group_by(window) %>%
    summarise(auc1 = get_auc(Y, pred_w1),
              auc2 = get_auc(Y, pred_w2),
              auc3 = get_auc(Y, pred_w3),
              auc4 = get_auc(Y, pred_w4)) %>%
    filter(window != 1) %>% 
    select(starts_with("auc"))
  auc_gfosr_l1[, ,m] <- as.matrix(auc_tb)

}

mean_auc_gfosr_l1 <- apply(auc_gfosr_l1, c(1, 2), mean)
colnames(mean_auc_gfosr_l1) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r auc_gfosr_l5}
for(m in 1:M){
  this_df <- pred_list_gfosr_l5[[m]]
  auc_tb <- this_df %>% 
    select(Y, starts_with("pred"), window) %>%
    group_by(window) %>%
    summarise(auc1 = get_auc(Y, pred_w1),
              auc2 = get_auc(Y, pred_w2),
              auc3 = get_auc(Y, pred_w3),
              auc4 = get_auc(Y, pred_w4)) %>%
    filter(window != 1) %>% 
    select(starts_with("auc"))
  auc_gfosr_l5[, ,m] <- as.matrix(auc_tb)

}

mean_auc_gfosr_l5 <- apply(auc_gfosr_l5, c(1, 2), mean)
colnames(mean_auc_gfosr_l5) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r table_sim1}
fgfpca1 <- rbind(mean_ise_fgfpca ,mean_auc_fgfpca) %>% as_tibble() %>%
  mutate(Window = rep(c("(0.2, 0.4]", "(0.4, 0.6]", "(0.6, 0.8]", "(0.8, 1.0]"), 2), .before=1)
gfosr_l5_1 <- rbind(mean_ise_gfosr_l5 ,mean_auc_gfosr_l5) %>% as_tibble()
gfosr_l1_1 <- rbind(mean_ise_gfosr_l1 ,mean_auc_gfosr_l1) %>% as_tibble()
adglmm1 <- rbind(mean_ise_adglmm ,mean_auc_adglmm) %>% as_tibble()

bind_cols(fgfpca1, gfosr_l5_1, gfosr_l1_1, adglmm1, .name_repair = "minimal") %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "fGFPCA" = 4, "GFOSR (L=5)" = 4, 
                     "GFOSR (L=1)" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" " = 1, "Maximum observation time" = 16)) %>%
  group_rows(index = c("ISE"= 4, "AUC" = 4)) %>%
  landscape()

# Small-scale simulation

I have used 100 subjects for training and testing, and repeated 500 times. When fitting GLMMadpative, I reduce the number of measurements in the training dataset to 1/10 by taking one every 10 observations. The prediction is on the original grid.

```{r load_sim2}
load(here("Data/SubSimOutput_GLMMadaptive.RData"))

load(here("Data/SubSimOutput_fGFPCA.RData"))
pred_subset_adglmm <- pred_subset_adglmm[!num_probs]
fit_time_subset_adglmm <- fit_time_subset_adglmm[!num_probs]
pred_time_subset_adglmm <- pred_time_subset_adglmm[!num_probs]

load(here("Data/SubSimOutput_GFOSR_L1.RData"))
pred_subset_gfosr_l1 <- pred_list_gfofr_subset
t_subset_gfosr_l1 <- t_vec_gfofr_subset
rm(pred_list_gfofr_subset, t_vec_gfofr_subset)

load(here("Data/SubSimOutput_GFOSR_L5.RData"))
pred_subset_gfosr_l5 <- pred_list_gfofr_subset
t_subset_gfosr_l5 <- t_vec_gfofr_subset
rm(pred_list_gfofr_subset, t_vec_gfofr_subset)

rand_id <- sample(101:200, size = 4)
```

## Figure

```{r fig_small_sim_paper, fig.height=8, fig.width=8}
bind_rows(
  pred_subset_fGFPCA[[1]] %>% filter(id %in% rand_id) %>% mutate(method="fGFPCA"),
  pred_subset_gfosr_l5[[1]] %>% filter(id %in% rand_id) %>% mutate(method = "GFOSR (L=5)") %>% 
    rename(pred0.2=pred_w1, pred0.4=pred_w2, pred0.6=pred_w3, pred0.8=pred_w4),
  pred_subset_gfosr_l1[[1]] %>% filter(id %in% rand_id) %>% mutate(method = "GFOSR (L=1)") %>%
    rename(pred0.2=pred_w1, pred0.4=pred_w2, pred0.6=pred_w3, pred0.8=pred_w4),
  pred_subset_adglmm[[1]] %>% filter(id %in% rand_id) %>% mutate(method = "GLMMadaptive")) %>%
  mutate_at(vars(eta_i, pred0.2, pred0.4, pred0.6, pred0.8), 
                .funs = function(x){exp(x)/(1+exp(x))}) %>%
  mutate(method=factor(method, 
         levels = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"))) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"), linetype = "dashed")+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linewidth=1, na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linewidth=1, na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linewidth=1, na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linewidth=1, na.rm=T)+
  facet_grid(rows = vars(id), cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "bottom")+
  scale_color_manual(values = cols)
```

```{r}
sep_plot <- bind_rows(
  pred_subset_fGFPCA[[1]] %>% filter(id==189) %>% mutate(method="fGFPCA"),
  pred_subset_gfosr_l5[[1]] %>% filter(id==189) %>% mutate(method = "GFOSR (L=5)") %>% 
    rename(pred0.2=pred_w1, pred0.4=pred_w2, pred0.6=pred_w3, pred0.8=pred_w4),
  pred_subset_gfosr_l1[[1]] %>% filter(id==189) %>% mutate(method = "GFOSR (L=1)") %>%
    rename(pred0.2=pred_w1, pred0.4=pred_w2, pred0.6=pred_w3, pred0.8=pred_w4),
  pred_subset_adglmm[[1]] %>% filter(id==189) %>% mutate(method = "GLMMadaptive")) %>%
  mutate_at(vars(eta_i, pred0.2, pred0.4, pred0.6, pred0.8), 
                .funs = function(x){exp(x)/(1+exp(x))}) %>%
  mutate(method=factor(method, 
         levels = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"))) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"), linetype = "dashed")+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linewidth=1, na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linewidth=1, na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linewidth=1, na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linewidth=1, na.rm=T)+
  facet_grid(cols = vars(method))+
  labs(col = "Maximum observation time", x = "t", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))
```

```{r, fig_small_sim_pre, fig.height=2, fig.width=8}
sep_plot+scale_color_manual(values = cols, guide="none")+
  #theme(legend.position = "bottom")+
  scale_color_manual(values = cols, guide = "none")
```

```{r, legend, fig.height=0.2, fig.width=8}
as_ggplot(ggpubr::get_legend(sep_plot+theme(legend.position = "bottom")+
                               scale_color_manual(values = cols)))
```

## ISE and AUC

```{r ise_subset}
## ISE container 
ise_fgfpca2 <- ise_adglmm2 <- ise_gfosr_l1_2 <- ise_gfosr_l5_2 <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M))
# dims: prediction window, max obs time, simulation iter

```{r ise_fGFPCA_subset}
for(m in 1:length(pred_subset_fGFPCA)){
  this_df <- pred_subset_fGFPCA[[m]]
  ise_tb_m <- this_df %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err")) %>% as.matrix()
  ise_fgfpca2[,,m] <- ise_tb_m
}

mean_ise_fgfpca2 <- apply(ise_fgfpca2, c(1, 2), mean)

colnames(mean_ise_fgfpca2) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r ise_GLMMadaptive_subset}
for(m in 1:length(pred_subset_adglmm)){
  this_df <- pred_subset_adglmm[[m]]
  ise_tb_m <- this_df %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err")) %>% as.matrix()
  ise_adglmm2[,,m] <- ise_tb_m
}

mean_ise_adglmm2<- apply(ise_adglmm2, c(1, 2), mean, na.rm = T)

colnames(mean_ise_adglmm2) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r ise_gfosr_l1_subset}
for(m in 1:length(pred_subset_gfosr_l1)){
  this_df <- pred_subset_gfosr_l1[[m]]
  ise_tb_m <- this_df %>%
    mutate(err1 = (pred_w1-eta_i)^2,
           err2 = (pred_w2-eta_i)^2,
           err3 = (pred_w3-eta_i)^2,
           err4 = (pred_w4-eta_i)^2) %>%
    select(id, t, starts_with("err"), window) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != 1) %>% 
    select(starts_with("err")) %>% as.matrix()
  ise_gfosr_l1_2[,,m] <- ise_tb_m
}

mean_ise_gfosr_l1_2<- apply(ise_gfosr_l1_2, c(1, 2), mean, na.rm = T)

colnames(mean_ise_gfosr_l1_2) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r ise_gfosr_l5_subset}
for(m in 1:length(pred_subset_gfosr_l5)){
  this_df <- pred_subset_gfosr_l5[[m]]
  ise_tb_m <- this_df %>%
    mutate(err1 = (pred_w1-eta_i)^2,
           err2 = (pred_w2-eta_i)^2,
           err3 = (pred_w3-eta_i)^2,
           err4 = (pred_w4-eta_i)^2) %>%
    select(id, t, starts_with("err"), window) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != 1) %>% 
    select(starts_with("err")) %>% as.matrix()
  ise_gfosr_l5_2[,,m] <- ise_tb_m
}

mean_ise_gfosr_l5_2 <- apply(ise_gfosr_l5_2, c(1, 2), mean, na.rm = T)

colnames(mean_ise_gfosr_l5_2) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r auc2}
## auc container 
auc_fgfpca2 <- auc_adglmm2 <- auc_gfosr_l1_2 <- auc_gfosr_l5_2 <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M))
```

```{r auc_fGFPCA_subset}
for(m in 1:length(pred_subset_fGFPCA)){
  this_df <- pred_subset_fGFPCA[[m]]
  auc_tb_m <- this_df %>%
  mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred0.2),
            auc2 = get_auc(Y, pred0.4),
            auc3 = get_auc(Y, pred0.6),
            auc4 = get_auc(Y, pred0.8)) %>%
  filter(window != "[0,0.2]") %>% 
  select(starts_with("auc")) %>% as.matrix()

  auc_fgfpca2[, , m] <- auc_tb_m

}

mean_auc_fgfpca2 <- apply(auc_fgfpca2, c(1,2), mean)
colnames(mean_auc_fgfpca2) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r auc_GLMMadaptive_subset}
for(m in 1:length(pred_subset_adglmm)){
  this_df <- pred_subset_adglmm[[m]]
  auc_tb_m <- this_df %>%
  mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred0.2),
            auc2 = get_auc(Y, pred0.4),
            auc3 = get_auc(Y, pred0.6),
            auc4 = get_auc(Y, pred0.8)) %>%
  filter(window != "[0,0.2]") %>% 
  select(starts_with("auc")) %>% as.matrix()

  auc_adglmm2[, , m] <- auc_tb_m

}

mean_auc_adglmm2 <- apply(auc_adglmm2, c(1,2), mean, na.rm = T)
colnames(mean_auc_adglmm2) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r auc_GFOSR_subset_l1}
for(m in 1:length(pred_subset_gfosr_l1)){
  this_df <- pred_subset_gfosr_l1[[m]]
  auc_tb_m <- this_df %>%
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred_w1),
            auc2 = get_auc(Y, pred_w2),
            auc3 = get_auc(Y, pred_w3),
            auc4 = get_auc(Y, pred_w4)) %>%
  filter(window != 1) %>% 
  select(starts_with("auc")) %>% as.matrix()

  auc_gfosr_l1_2[, , m] <- auc_tb_m

}

mean_auc_gfosr_l1_2 <- apply(auc_gfosr_l1_2, c(1,2), mean)
colnames(mean_auc_gfosr_l1_2) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r auc_GFOSR_subset_l5}
for(m in 1:length(pred_subset_gfosr_l5)){
  this_df <- pred_subset_gfosr_l5[[m]]
  auc_tb_m <- this_df %>%
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred_w1),
            auc2 = get_auc(Y, pred_w2),
            auc3 = get_auc(Y, pred_w3),
            auc4 = get_auc(Y, pred_w4)) %>%
  filter(window != 1) %>% 
  select(starts_with("auc")) %>% as.matrix()

  auc_gfosr_l5_2[, , m] <- auc_tb_m

}

mean_auc_gfosr_l5_2 <- apply(auc_gfosr_l5_2, c(1,2), mean)
colnames(mean_auc_gfosr_l5_2) <- c("0.2", "0.4", "0.6", "0.8")
```

>>>>

set.seed(1114)

@@

# code 
source(here("Code/PredEval.R"))

## prediction window 
window <- seq(0, 1, by = 0.2)
M <- 5

@@

```{r load_sim1}
load(here("Data/TrialRun/SimOutput_fGFPCA.RData"))
load(here("Data/TrialRun/SimOutput_GLMMadaptive.RData"))
load(here("Data/TrialRun/SimOutput_GFOSR_L1.RData"))
load(here("Data/TrialRun/SimOutput_GFOSR_L5.RData"))

@@

```{r DataFormat}
pred_list_fGFPCA <- lapply(pred_list_fGFPCA, function(x){x %>% select(-bin)})
name_vec <- colnames(pred_list_fGFPCA[[1]])
pred_list_fGFPCA <- lapply(pred_list_fGFPCA, 
                           function(x){
                      x[x$t<=0.2, c("pred0.2", "pred0.2_lb", "pred0.2_ub")] <- NA
                      x[x$t<=0.4, c("pred0.4", "pred0.4_lb", "pred0.4_ub")] <- NA
                      x[x$t<=0.6, c("pred0.6", "pred0.6_lb", "pred0.6_ub")] <- NA
                      x[x$t<=0.8, c("pred0.8", "pred0.8_lb", "pred0.8_ub")] <- NA
                      return(x)    
                       })

pred_list_GLMMad <- lapply(pred_list_GLMMad, function(x){
  colnames(x) <- name_vec
  return(x)
})

pred_list_gfofr <- lapply(pred_list_gfofr, function(x){
  x <- x %>% select(-window)
  colnames(x) <- name_vec
  return(x)
})

pred_list_gfofr_l5 <- lapply(pred_list_gfofr_l5, function(x){
  x <- x %>% select(-window)
  colnames(x) <- name_vec
  return(x)
})

@@

```{r large_sim_plot, fig.height=8, fig.width=8}
bind_rows(
  pred_list_fGFPCA[[1]] %>% filter(id %in% rand_id) %>% 
    mutate(method="fGFPCA"),
  pred_list_GLMMad[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GLMMadaptive"),
  pred_list_gfofr[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=1)"),
  pred_list_gfofr_l5[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=5)") 
) %>% 
  mutate_at(vars(eta_i, starts_with("pred")), 
                .funs = function(x){exp(x)/(1+exp(x))}) %>%
  mutate(method=factor(method, 
         levels = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"))) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.2_lb, ymax = pred0.2_ub,
                  col = "0.2", fill = "0.2", alpha = 0.1),
              linetype="dashed")+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.4_lb, ymax = pred0.4_ub,
                  col = "0.4", fill = "0.4", alpha = 0.1),
              linetype="dashed")+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.6_lb, ymax = pred0.6_ub,
                  col = "0.6", fill = "0.6", alpha = 0.1),
              linetype="dashed")+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.8_lb, ymax = pred0.8_ub,
                  col = "0.8", fill = "0.8", alpha = 0.1),
              linetype="dashed")+
  guides(alpha = "none", col="none")+
  facet_grid(rows = vars(id), cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "bottom")+
  scale_color_manual(values = cols)
```

## Preformance

Please note that here, the GLMM has a **square** time for both fixed effect and random effect.

### Time (minutes)

```{r}
data.frame(Method = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"), 
           Time = c(mean(time_fGFPCA),
                    mean(time_gfofr_l5),
                    mean(time_gfofr),
                    mean(time_GLMMad))) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F)
```

### ISE

```{r}
cbind(calc_ISE(pred_list_fGFPCA, window),
      calc_ISE(pred_list_gfofr, window),
      calc_ISE(pred_list_gfofr_l5, window),
      calc_ISE(pred_list_GLMMad, window)) %>%
  data.frame(window = c("[0, 0.2]", "(0,2, 0.4]", "(0.4, 0.6]", 
                    "(0.6, 0.8]","(0.8, 1]"),
             ., 
             check.names = F) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "fGFPCA" = 4, "GFOSR (L=5)" = 4, 
                     "GFOSR (L=1)" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" " = 1, "Maximum observation time" = 16)) %>%
  landscape()
```

It looks like the predictive performance can be seriously worse if the prediction window is far from the observation window.

### AUC

```{r}
cbind(calc_AUC(pred_list_fGFPCA, window),
      calc_AUC(pred_list_gfofr, window),
      calc_AUC(pred_list_gfofr_l5, window),
      calc_AUC(pred_list_GLMMad, window)) %>%
  data.frame(window = c("[0, 0.2]", "(0,2, 0.4]", "(0.4, 0.6]", 
                    "(0.6, 0.8]","(0.8, 1]"),
             ., 
             check.names = F) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "fGFPCA" = 4, "GFOSR (L=5)" = 4, 
                     "GFOSR (L=1)" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" " = 1, "Maximum observation time" = 16)) %>%
  landscape()
```

It seems that the GFOSR models, while are the fastest, also performs the worst in AUC.

### Prediction interval

Not sure how to display. Maybe start with if the prediction interval covers the truth? That is, coverage rate at each time point, averaged over all simulation and subjects?

```{r, fig.height=4, fig.width=16}
bind_rows(calc_predint_cover(pred_list_fGFPCA) %>% mutate(method = "fGFPCA"),
          calc_predint_cover(pred_list_gfofr_l5) %>% mutate(method = "GFOSR (L=5)"),
          calc_predint_cover(pred_list_gfofr) %>% mutate(method = "GFOSR (L=1)"),
          calc_predint_cover(pred_list_GLMMad) %>% mutate(method = "GLMMadaptive")) %>%
  ggplot()+
  geom_line(aes(x=t, y=cover0.2, col = "0.2"), na.rm = T)+
  geom_line(aes(x=t, y=cover0.4, col = "0.4"), na.rm = T)+
  geom_line(aes(x=t, y=cover0.6, col = "0.6"), na.rm = T)+
  geom_line(aes(x=t, y=cover0.8, col = "0.8"), na.rm = T)+
  facet_grid(cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="Coverage rate")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "bottom")+
  scale_color_manual(values = cols)
```
